---
title: "Project 1"
author: "Zhongcheng Tu"
date: "2022-09-17"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

load packages
```{r, warning=FALSE}
library(syuzhet)
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
```

read data
```{r, warning=FALSE}
philosophy_data <- read.csv("philosophy_data.csv")
head(philosophy_data)
```

```{r, warning=FALSE}
school_sentence <- philosophy_data[c(3, 5)]
head(school_sentence)
```
divide by school
```{r, warning=FALSE}
# divide by school: analytic, aristotle, capitalism, communism, continental,
# empiricism, feminism, german_idealism, nietzsche, phenomenology, plato, 
# rationalism, stoicism.
analytic <- philosophy_data[philosophy_data$school == "analytic",
                            ]$sentence_str
aristotle <- philosophy_data[philosophy_data$school == "aristotle",
                             ]$sentence_str
capitalism <- philosophy_data[philosophy_data$school == "capitalism",
                              ]$sentence_str
communism <- philosophy_data[philosophy_data$school == "communism",
                             ]$sentence_str
continental <- philosophy_data[philosophy_data$school == "continental",
                               ]$sentence_str
empiricism <- philosophy_data[philosophy_data$school == "empiricism",
                              ]$sentence_str
feminism <- philosophy_data[philosophy_data$school == "feminism",
                            ]$sentence_str
german_idealism <- philosophy_data[philosophy_data$school == "german_idealism",
                                   ]$sentence_str
nietzsche <- philosophy_data[philosophy_data$school == "nietzsche",
                             ]$sentence_str
phenomenology <- philosophy_data[philosophy_data$school == "phenomenology",
                                 ]$sentence_str
plato <- philosophy_data[philosophy_data$school == "plato",
                         ]$sentence_str
rationalism <- philosophy_data[philosophy_data$school == "rationalism",
                               ]$sentence_str
stoicism <- philosophy_data[philosophy_data$school == "stoicism",
                            ]$sentence_str
```


find the emotion trend by school, return a table with proportion of different emotions
```{r, warning=FALSE}
emotion_proportion <- function(school, sample_size = 100){
  result = colSums(get_nrc_sentiment(sample(school, sample_size)))
  result = result / sum(result)
  return(result)
}

emotion_proportion(stoicism)
overall_emotion_by_school = 
  data.frame(analytic = emotion_proportion(analytic), 
             aristotle = emotion_proportion(aristotle), 
             capitalism = emotion_proportion(capitalism), 
             communism = emotion_proportion(communism), 
             continental = emotion_proportion(continental), 
             empiricism = emotion_proportion(empiricism), 
             feminism = emotion_proportion(feminism), 
             german_idealism = emotion_proportion(german_idealism), 
             nietzsche = emotion_proportion(nietzsche), 
             phenomenology = emotion_proportion(phenomenology), 
             plato = emotion_proportion(plato), 
             rationalism = emotion_proportion(rationalism), 
             stoicism = emotion_proportion(stoicism))

overall_emotion_by_school
```

show by boxplot
```{r, warning=FALSE}
barplot(t(as.matrix(overall_emotion_by_school)),
        main = "Grouped barchart",ylab = "Frequency",
        names.arg = rownames(overall_emotion_by_school),
        col = c("antiquewhite", "aquamarine", "blue", "blueviolet", 
        "burlywood", "chartreuse", "cornflowerblue", "cyan", 
        "darkolivegreen2", "darkorchid1", 
        "deepskyblue", "firebrick1", "deeppink"),
        legend.text = colnames(overall_emotion_by_school),
        legend = TRUE, args.legend = list(bty = "n", x = "top", ncol = 3),
        beside = TRUE)
```

From the boxplot, it can be observed that some school shows a relatively strong trend in certain field of emotion. For example, German idealism and phenomenology shows a strong positive trend, while continental school shows more words in anger, fear, or sadness.

